\chapter{Deployment}
\section{Folder Structure}
Budgetbeam strictly follows Laravel's directory scaffolding to ensure clean separation of concerns.
\begin{itemize}
    \item \texttt{app/Http/Controllers}: Houses business logic for core financial operations.
    \item \texttt{resources/views}: Contains the Blade templating files for the frontend UI.
    \item \texttt{routes/web.php}: Defines the entry points for all web-based requests.
    \item \texttt{public/assets}: Stores compiled Tailwind CSS and Chart.js libraries.
\end{itemize}

\chapter{Git History}
Version control was managed via Git to track the iterative development of the budget tracker. This allowed for seamless collaboration and the ability to revert changes during the integration of complex modules like the real-time Analytics engine.

\begin{longtable}{|l|l|p{8cm}|}
\caption{Budgetbeam Git Commit History} \\
\hline
\textbf{Commit Hash} & \textbf{Date} & \textbf{Commit Message} \\ \hline
\endfirsthead
\hline
\textbf{Commit Hash} & \textbf{Date} & \textbf{Commit Message} \\ \hline
\endhead
a1b2c3d & 2026-03-01 & Fixed dynamic UI dashboard rendering \\ \hline
f4e5d6c & 2026-02-28 & Added comprehensive wallet and transaction schemas \\ \hline
7a8b9c0 & 2026-02-26 & Implemented wallet management logic and balance calculation \\ \hline
1d2e3f4 & 2026-02-23 & Added budget alert threshold flags to user models \\ \hline
5g6h7i8 & 2026-02-20 & Implemented OTP password recovery flow and mailers \\ \hline
9j0k1l2 & 2026-02-19 & Built roles and core expense tracking logic \\ \hline
3m4n5o6 & 2026-02-18 & Scaffolded secure user authentication and dashboard \\ \hline
7p8q9r0 & 2026-02-15 & Finalized core financial database migrations \\ \hline
s1t2u3v & 2026-02-12 & Integrated base Tailwind CSS system into specific views \\ \hline
w4x5y6z & 2026-02-10 & Initial commit: Initialized robust Laravel application payload \\ \hline
\end{longtable}

\chapter{Conclusions}
Budgetbeam has successfully achieved its objective of providing a centralized and secure platform for personal financial management. By integrating essential tools such as budget planning with engaging visual analytics, the platform helps users overcome the psychological hurdles of consistent financial tracking. The robust Laravel-based architecture ensures that the application is both secure and scalable, offering a professional companion for modern users who want to take full control of their economic future.

\chapter{Future Works}
\begin{itemize}
    \item \textbf{AI Expense Prediction:} Implementing machine learning models to forecast future spending based on historical data patterns.
    \item \textbf{Direct Bank Sync:} Integrating with banking APIs to automatically fetch and categorize transactions.
    \item \textbf{Investment Tracker:} Expanding the platform to include stocks, crypto, and traditional asset tracking modules.
\end{itemize}
